Automated Dynamic Slice Backsolving

### 2014-03-21 docs/paper/fsuthesis/thesis-template/paper.tex
working on figures and testing,results

Secrets of length 1 to 50 were tested at regular intervals. It appears that, aside from some constant overhead, that test cases generated and time required to crack the binary  rise linearly with password length. The constant overhead is probably introduced from overtaint.

@@

\begin{figure}
\caption{Fig. 1}
\begin{tikzpicture}
\begin{axis}[
    title={Oracle Attack},
    xlabel={Secret Length},
    ylabel={Test cases},
    xmin=0, xmax=55,
    ymin=10, ymax=100,
    xtick={0,10,20,30,40,50},
    ytick={20,30,40,50,60,70,80,90,100},
    ymajorgrids=true,
    grid style=dashed,
]

@@

\begin{tikzpicture}
\begin{axis}[
    title={Oracle Attack},
    xlabel={Secret Length},
    ylabel={Time Elapsed (seconds)},
    xmin=0, xmax=55,
    ymin=10, ymax=200,
    xtick={0,10,20,30,40,50},
    ytick={0,20,30,40,50,60,80,100,120,140,160,180,200},
    ymajorgrids=true,
    grid style=dashed,
]

\addplot[
    color=red,
    mark=square,
    ]
    coordinates {
    		(1,0) % TODO time these first couple
    		(4,0)
    		(7,0)
    		(10,0)
    		(15,0)
    		(20, 0)
    		(25, 101) 
    		(30, 112)
    		(35, 129) 
    		(40, 140)
    		(45, 157) 
    		(50, 172) 
    }; 
\end{axis}
\end{tikzpicture}

>>>>

This bears a strong resemblance to the classic oracle attack in cryptography. Note, however, that stubble would be unable to reason effectively about cryptographic hashes or encryption because of properties like one-way functions and the avalanche effect.

In a traditional oracle attack, the adversary can derive a secret by testing one character at a time. This means an attacker can expect success within $\frac{mn}{2}$ tries on average, where m is the number of character possiblities and n is the length of the secret. Dumb fuzzers, which are unable to reason about the execution paths in a binary, do much worse by mutating random bytes and hoping to hit upon the secret by chance. This strategy can expect success within $\frac{m^n}{2}$ tries on average, since m-many possibilities must be tested for each byte in the secret independently. Stubble performs similarly to an attacker with access to an oracle, although because execution slices are backsolved its time complexity has a smaller constant than $\frac{m}{2}$. Expected number of tries is linear with secret length, as with an oracle attack, but stubble requires roughly two tries per byte, instead of having to test for all possible m.

Secrets of length 1 to 50 were tested at regular intervals. It appears that, aside from some constant overhead, that test cases generated and time required to crack the binary rise linearly with password length as expected. The constant overhead is probably introduced from overtaint, which itself likely comes from dynamically linked libraries which are opened and read, and thereby mistakenly introduced as tainted input.

@@

\begin{figure}
\caption{Secret Guessing Test Cases}
\begin{tikzpicture}
\begin{axis}[
    title={Oracle Attack},
    xlabel={Secret Length},
    ylabel={Test cases},
    xmin=0, xmax=55,
    ymin=10, ymax=100,
    xtick={0,10,20,30,40,50},
    ytick={20,30,40,50,60,70,80,90,100},
    ymajorgrids=true,
    grid style=dashed,
]

@@

\begin{figure}
\caption{Secret Guessing Time Elapsed}
\begin{tikzpicture}
\begin{axis}[
    title={Oracle Attack},
    xlabel={Secret Length},
    ylabel={Time Elapsed (seconds)},
    xmin=0, xmax=55,
    ymin=10, ymax=200,
    xtick={0,10,20,30,40,50},
    ytick={0,20,30,40,50,60,80,100,120,140,160,180,200},
    ymajorgrids=true,
    grid style=dashed,
]

\addplot[
    color=red,
    mark=square,
    ]
    coordinates {
    		(1,0) % TODO time these first couple
    		(4,0)
    		(7,0)
    		(10,0)
    		(15,0)
    		(20, 0)
    		(25, 101) 
    		(30, 112)
    		(35, 129) 
    		(40, 140)
    		(45, 157) 
    		(50, 172) 
    }; 
\end{axis}
\end{tikzpicture}
\end{figure}
